---
title: "Data607 Wk10 assignment"
author: "angel"
date: "2024-03-31"
output: html_document


---
#Task : recreate example code from chapter 2 , replicate using new corpus


#2.1 The sentiments datasets
```{r}

library(tidytext)

get_sentiments("afinn")
```

```{r}
get_sentiments("bing")
```
yes
```{r}
get_sentiments("nrc")
```



#2.2 Sentiment analysis with inner join

```{r}
library(janeaustenr)
library(dplyr)
library(stringr)

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
```





```{r}
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
```

```{r}
library(tidyr)
jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```





```{r}
library(ggplot2)

ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```


#2.3 Comparing the three sentiment dictionaries
```{r}
pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")

pride_prejudice
```


```{r}
afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  pride_prejudice %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  pride_prejudice %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```

```{r}
bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```

```{r}
get_sentiments("nrc") %>% 
  filter(sentiment %in% c("positive", "negative")) %>% 
  count(sentiment)
```

```{r}
get_sentiments("bing") %>% 
  count(sentiment)
```
#2.4 Most common positive and negative words


```{r}
bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts
```

```{r}
bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```

```{r}
custom_stop_words <- bind_rows(tibble(word = c("miss"),  
                                      lexicon = c("custom")), 
                               stop_words)

custom_stop_words
```
#2.5 Wordclouds
```{r}
library(wordcloud)

tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```

```{r}
library(reshape2)

tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```





# Replicate with books from Charles dickens
```{r}
library(gutenbergr)




# Display the first few rows of the metadata dataframe
glimpse(gutenberg_works())

```


#download books by charles dickens
```{r}
cd <- gutenberg_works(author == "Dickens, Charles")
cd_works <- cd[cd$gutenberg_id > 42000, ]
cd_books <- gcd_books <- gutenberg_download(cd_works$gutenberg_id, meta_fields = "title")
```






#tidy

```{r}
cd_books <- cd_books %>%
 mutate( linenumber = row_number(),
    chapter = cumsum(str_detect(text, regex("^([\\divxlc])+$", ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
```




```{r}


cd_sentiment <- cd_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(title, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```



#sentiment scores
```{r}
library(ggplot2)



ggplot(cd_sentiment, aes(index, sentiment, fill = title)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~title, ncol = 2, scales = "free_x")
```





#Sentiment analysis with inner join
```{r}
nrc_j <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

cd_books %>%
  filter(title == "A Child's Dream of a Star") %>%
  inner_join(nrc_j) %>%
  count(word, sort = TRUE)
```



```{r}
Childs_dream <- cd_books %>% 
  filter(title == "A Child's Dream of a Star")
```



#compare the three sentiments
```{r}
aff <- Childs_dream  %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_nrc <- bind_rows(
  Childs_dream  %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  Childs_dream  %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```

```{r}
bind_rows(aff, 
          bing_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```




#most common negative and positive words

```{r}
word_counts <- cd_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
```



# alot more positive words than negative
```{r}
word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```




#word clouds

```{r}
cd_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```


```{r}
cd_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```



# conclusion : overall, Charles Dickens book seem to have positive sentiments.